\newpage

\thispagestyle{empty}

\begin{de}
\section*{Abriss}
Den Inhalt dieser Bachelorarbeit bildet eine kurze Einf\"uhrung in die Modultheorie. Im ersten Abschnitt werden die grundlegenden Begriffe der Modultheorie eingef\"uhrt und die ersten elementaren Eigenschaften bewiesen. Wir werden sehen, dass sowohl Ringe mit 1 als auch Vektorr\"aume eine Modulstruktur tragen. Besonders deutlich tritt dieser Zusammenhang zwischen Moduln und Ringen hervor, wenn wir bereits bekannte Ei\-gen\-schaf\-ten von Ringen -- wie den Homomorphiesatz -- auf Moduln verallgemeinern. Der zweite Teil dieser Arbeit widmet sich Er\-zeug\-en\-den\-sys\-tem\-en, Basen und linearer Unabh\"angigkeit und versteht sich als Vergleich zwischen Moduln und Vektorr\"aumen.
\end{de}
\vspace{1.5cm}
\section*{Abstract}
The content of this bachelor thesis is a brief introduction to module theory. In the first section the basic definitions are introduced and some elementary properties are proven. We will see that unitary rings as well as vector spaces carry a module structure and will generalize well-known results of rings on modules. The second section deals with generating sets, bases and linear independence and can be viewed as a comparison between vector spaces and modules.

\newpage
\chapter*{\contentsname}

\printcontents[parts]{1}{}{}


\chapter{Definitions and Elementary Properties}

	Closely following \cite[Chap.VII]{jantzen2005algebra} we will start with a series of definitions and notations.
	
	\section{Basic Definitions}
	
		\input{./parts/content/ScalarMultiplication}

	\section{Module-Homomorphisms}
		
		\input{./parts/content/ModuleHomomorphisms}

	\section{Quotient Modules and Isomorphism Theorems}

		\input{./parts/content/QuotientModules}
		
	\section{Direct Sums and Products}
	
		\input{./parts/content/DirectSumsAndProducts}
		
\chapter{Generating Sets and Bases of Modules} \label{sec.GenSets}

	\section{Basic Definitions}

		\input{./parts/content/GeneratingSets}

	\section{Free Modules}
	
		\input{./parts/content/FreeModules}
		
	\section{Homomorphisms of Free Modules and Matrices}
	
		\input{./parts/content/FreeModulesAndMatrices}



\vspace{\fill}
\begingroup
\sloppy
\printbibliography[heading=subbibliography]
\endgroup
